sampling

### 2021-09-22 code/ms1_sampling.Rmd
analysis reboot

site_data <- read_csv("../data/processed_data/site_data.csv") %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean, elev.class, elev.class2)) %>% 
  mutate(site = factor(site),
         tree_line = factor(tree_line))
```

@@

## Visualize
```{r message=FALSE, warning=FALSE}
samplingplot1 <- ggplot(visitation_sampling, aes(x = year(date))) +
  geom_bar(fill = "gray60") +
  ylab("Total bumble bees\nobserved") +
  theme_light(11) +
  theme(axis.title.x = element_blank())

samplingplot2 <- ggplot(bb_obs_per_sample, aes(x = year)) +
  geom_bar(fill = "gray60") +
  ylab("Total samples") +
  theme_light(11) +
  theme(axis.title.x = element_blank())

samplingplot3 <- ggplot(bb_obs_per_sample, aes(x = year, y = obs)) +
  geom_violin(draw_quantiles = 0.5, fill = "gray60", color = NA) +
  geom_boxplot(fill = NA) +
  #geom_density(outline.type = "full", position = "fill") +
  ylab("Bumble bees\nobserved / sample") +
  #xlab(NULL) +
  theme_light(11) +
  theme(axis.title.x = element_blank())

samplingplot4 <- ggplot(bb_obs_per_sample, aes(as_date(yday(date)), elev.mean/10)) +
  geom_point(size = 1, aes(alpha = obs)) +
  facet_wrap(~year) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_alpha_continuous(name = "Bumble bees\nobserved") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  theme_light(11) +
  labs(x = NULL,
       y = "Elevation (m x 10)")

@@

ggsave("../ms_1/figures/samplingplot.pdf", height = 6, width = 10.5)
ggsave("../ms_1/figures/samplingplot.png", height = 6, width = 10.5)
```

>>>>

site_data <- read_csv("../data/processed_data/site_data.csv") %>%
  semi_join(visitation_sampling) %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean, elev.class, elev.class2)) %>% 
  mutate(site = factor(site),
         tree_line = factor(tree_line))
```

@@

## Visualize
```{r message=FALSE, warning=FALSE}
samplingplot1 <- ggplot(visitation_sampling, aes(x = year(date))) +
  geom_bar(fill = "gray60") +
  ylab("Total bumble bees\nobserved") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot2 <- ggplot(bb_obs_per_sample, aes(x = year)) +
  geom_bar(fill = "gray60") +
  ylab("Total samples") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot3 <- ggplot(bb_obs_per_sample, aes(x = year, y = obs)) +
  geom_violin(draw_quantiles = 0.5, fill = "gray60", color = NA) +
  geom_boxplot(fill = NA) +
  ylab("Bumble bees\nobserved / sample") +
  theme_light(13) +
  theme(axis.title.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank())

samplingplot4 <- ggplot(bb_obs_per_sample, aes(as_date(yday(date)), elev.mean)) +
  geom_point(size = 1, aes(alpha = obs)) +
  facet_wrap(~year) +
  scale_alpha_continuous(name = "Bumble bees\nobserved") +
  scale_x_date(date_labels = "%b", breaks = as_date(c("1970-04-01", "1970-05-01", "1970-06-01",
                                                    "1970-07-01", "1970-08-01", "1970-09-01"))) +
  theme_light(13) +
  labs(x = NULL,
       y = "Elevation [m]") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank())

@@

ggsave("../ms_1/figures/fig2.pdf", samplingplot, height = 6, width = 10.5)
```
